---
title: "Machine Learning - Final project (project 10)"
author: "Bazile Cédric and Jain Khushi"
format: pdf
editor: visual
---

```{r}
#Libraries
here::i_am("Dauphine-ML-project-2024-2025.Rproj")
library(here)
library(readr)

## Data management
library(dplyr)
library(tidyr)
library(data.table)
library(stringr)
library(knitr)


## Graphics libraries
library(ggplot2)
library(scales)
library(plotly)

## ML
library(torch)
```

## Introduction

## Cleaning phase

```{r}
#Learning data set

## Import data
learn_df <- read_csv("Data - source/project-10-files/learn_dataset.csv")

##Check for NA
learn_df %>%  summarise_all(~ sum(is.na(.))) # No missing data

# Test dataset
## Import data
test_df <- read_csv("Data - source/project-10-files/test_dataset.csv")
any(duplicated(learn_df$KEY_PRIMARY)) 

##Check for NA
test_df %>%  summarise_all(~ sum(is.na(.))) # No missing data
any(duplicated(test_df$KEY_PRIMARY)) 
```

The principal datasets, both from the learning and testing phases, do not contain missing values or duplicates. However, as indicated in the instructions, a large number of missing values exist when adding the additional data on retirement, sports, and jobs.

```{r Create_the_dataframe_learning_data_part_one}

# Import additional data

learn_emp_type <- read_csv("Data - source/project-10-files/learn_dataset_emp_type.csv")

learn_job <- read_csv("Data - source/project-10-files/learn_dataset_job.csv")

learn_retired_former <- read_csv("Data - source/project-10-files/learn_dataset_retired_former.csv")

learn_retired_jobs <- read_csv("Data - source/project-10-files/learn_dataset_retired_jobs.csv")

learn_retired_pension <- read_csv("Data - source/project-10-files/learn_dataset_retired_pension.csv")

learn_sport <- read_csv("Data - source/project-10-files/learn_dataset_sport.csv")

# Chekcing for duplicate
 
any(duplicated(learn_emp_type$KEY_PRIMARY))
any(duplicated(learn_job$KEY_PRIMARY))
any(duplicated(learn_retired_former$KEY_PRIMARY))
any(duplicated(learn_retired_jobs$KEY_PRIMARY))
any(duplicated(learn_retired_pension$KEY_PRIMARY))
any(duplicated(learn_sport$KEY_PRIMARY))
# No duplicates found




```

```{r Create_the_dataframe_learning_data_part_two}
# Merger with left join
learn_merged <- learn_df %>%
  left_join(learn_emp_type, by = "PRIMARY_KEY") %>%
  left_join(learn_job, by = "PRIMARY_KEY") %>%
  left_join(learn_retired_former, by = "PRIMARY_KEY") %>%
  left_join(learn_retired_jobs, by = "PRIMARY_KEY") %>%
  left_join(learn_retired_pension, by = "PRIMARY_KEY") %>%
  left_join(learn_sport, by = "PRIMARY_KEY") %>% 

   mutate(TYPE_CONTRACT = ifelse(is.na(TYPE_OF_CONTRACT.x), TYPE_OF_CONTRACT.y, TYPE_OF_CONTRACT.x),
         Working_hours = ifelse(is.na(Working_hours.x), Working_hours.y, Working_hours.x),
         Work_condition = ifelse(is.na(Work_condition.x), Work_condition.y, Work_condition.x),
         company_category = ifelse(is.na(company_category.x), company_category.y, company_category.x),
         ECO_SECT = ifelse(is.na(ECO_SECT.x), ECO_SECT.y, ECO_SECT.x),
         job_desc = ifelse(is.na(job_desc.x), job_desc.y, job_desc.x),
         employee_count = ifelse(is.na(employee_count.x), employee_count.y, employee_count.x),
         Job_dep = ifelse(is.na(Job_dep.x), Job_dep.y, Job_dep.x),
         job_category = ifelse(is.na(job_category.x), job_category.y, job_category.x)) %>%
  
  select(-ends_with(".x"), -ends_with(".y"))
```

```{r Create_the_dataframe_test_data_part_one}

# Import additional data

test_emp_type <- read_csv("Data - source/project-10-files/test_dataset_emp_type.csv")

test_job <- read_csv("Data - source/project-10-files/test_dataset_job.csv")

test_retired_former <- read_csv("Data - source/project-10-files/test_dataset_retired_former.csv")

test_retired_jobs <- read_csv("Data - source/project-10-files/test_dataset_retired_jobs.csv")

test_retired_pension <- read_csv("Data - source/project-10-files/test_dataset_retired_pension.csv")

test_sport <- read_csv("Data - source/project-10-files/test_dataset_sport.csv")

# Chekcing for duplicate
 
any(duplicated(test_emp_type$KEY_PRIMARY))
any(duplicated(test_job$KEY_PRIMARY))
any(duplicated(test_retired_former$KEY_PRIMARY))
any(duplicated(test_retired_jobs$KEY_PRIMARY))
any(duplicated(test_retired_pension$KEY_PRIMARY))
any(duplicated(test_sport$KEY_PRIMARY))
# No duplicates found

```

```{r Create_the_dataframe_test_data_part_two}

# Merger with left join
test_merged <- test_df %>%
  left_join(test_emp_type, by = "PRIMARY_KEY") %>%
  left_join(test_job, by = "PRIMARY_KEY") %>%
  left_join(test_retired_former, by = "PRIMARY_KEY") %>%
  left_join(test_retired_jobs, by = "PRIMARY_KEY") %>%
  left_join(test_retired_pension, by = "PRIMARY_KEY") %>%
  left_join(test_sport, by = "PRIMARY_KEY")

```

```{r NA_tables}

# List of the column of the main dataset : this list will be used to keep only columns of the additional dataset in order to see the number and frequency of NA
learn_original_columns <- colnames(learn_df)
test_original_columns <- colnames(test_df)

# Learning set : Number of NA for each column
learn_na_count <- learn_merged %>%
  select(-all_of(learn_original_columns)) %>%  
  summarise(across(everything(), ~ as.integer(sum(is.na(.))))) %>%
  mutate(Statistics = "Learning set : count")  # Addition of a column to name the created statistics

# Learning set : % of NA for each colummn
learn_na_percentage <- learn_merged %>%
  select(-all_of(learn_original_columns)) %>%  
  summarise(across(everything(), ~ as.integer(mean(is.na(.))*100))) %>%
  mutate(Statistics = "Learning set : percentage")  

# Test set : Number of NA for each column
test_na_count <- test_merged %>%
  select(-all_of(test_original_columns)) %>%  
  summarise(across(everything(), ~ as.integer(sum(is.na(.))))) %>%
  mutate(Statistics = "Test set : count")  # Addition of a column to indicate the stat

# Test set : % of NA for each colummn
test_na_percentage <- test_merged %>%
  select(-all_of(test_original_columns)) %>%  
  summarise(across(everything(), ~ as.integer(mean(is.na(.))*100))) %>%
  mutate(Statistics = "Test set : percentage") 

# Creation of the final table
na_sum_table <- bind_rows(learn_na_count, learn_na_percentage, test_na_count, test_na_percentage) %>% 
  relocate(Statistics, .before = everything())

print(na_sum_table)
```

In addition to the learning and test dataset, we also used to additional dataset :

-   the variable "community_size" of "city_pop" : our hypothezis is even if the target variable is not described demographic size of a town has strong correlation with market size, job and available infrastructure and thus information that can probably impact this targert variable;

-   the variable "town_type" of the dataset "city_adm" : our hypothesis is that key cities like state capital or "préfecture" can benefit from greater investment and infrastucture. Similarly, because of their historical attractivity that they add be chosen as "préfecture";

-   and, the variable "dep" of the dataset "city_adm" in order to take into account potential departemental variation.

No missing values were found to report.

```{r Addition_of_demographic_data}
# Importation of the  dataset

city_adm <- read_csv("Data - source/project-10-files/city_adm.csv", 
                     col_types = cols(INSEE = col_character())) # the option col_types makes sure that INSEE's code are treated as characters what was not automatically the case this time during importation. 

city_pop <- read_csv("Data - source/project-10-files/city_pop.csv", 
    col_types = cols(INSEE = col_character()))


# Merging
learn_merged <- learn_merged %>% 
  left_join(city_adm, by = "INSEE") %>% 
  left_join(city_pop, by = "INSEE")

test_merged <- test_merged %>% 
  left_join(city_adm, by = "INSEE") %>% 
  left_join(city_pop, by = "INSEE")

# Checking NA for new data
col_demo_data <- colnames(left_join(city_adm, city_pop, by = "INSEE")) #column names of the new data

demo_learn_na_count <- learn_merged %>%
  select(col_demo_data) %>%  
  summarise(across(everything(), ~ as.integer(sum(is.na(.))))) %>%
  mutate(Statistics = "Learning set : count")


demo_test_na_count <- test_merged %>%
  select(col_demo_data) %>%  
  summarise(across(everything(), ~ as.integer(sum(is.na(.))))) %>%
  mutate(Statistics = "Test set : count")


demo_na_sum_table <- bind_rows(demo_learn_na_count, demo_test_na_count) 

# Removing intermediary columns
rm(col_demo_data)
rm(demo_test_na_count)
rm(demo_learn_na_count)
```

# N/A

```{r Addition_of_the_translation_of_the_code, results = "hide"}
################################     Town type       ###############################

#Translation
learn_merged_uncoded <- learn_merged %>%
  mutate(town_type_translated = case_when(
    grepl("Commune simple", town_type) ~ "Simple municipality",
    grepl("Chef-lieu canton", town_type) ~ "Canton capital",
    grepl("Préfecture de région", town_type) ~ "Regional prefecture",
    grepl("Préfecture", town_type) ~ "Prefecture",
    grepl("Sous-préfecture", town_type) ~ "Sub-prefecture",
    grepl("Capitale d'état", town_type) ~ "State capital",
    TRUE ~ town_type  # Conserve la valeur d'origine si non traduite
  ))

# Display the comparison of unique French values with their translations to check if there are any mistakes
comparison_table <- learn_merged_uncoded %>%
  select(town_type, town_type_translated) %>%
  distinct()

################################     Code Act       ################################
#Import
code_act <- read_csv("Data - source/project-10-files/code/code_act.csv")

#Merging
learn_merged_uncoded <- merge(learn_merged_uncoded, code_act, by.x = "act", by.y = "Code", all.x = TRUE, all.y = FALSE)
sum(is.na(learn_merged_uncoded$Libellé)) #no missing values

# Translation of the "Libellé"
learn_merged_uncoded <- learn_merged_uncoded %>%
  mutate(act_translated = case_when(
    grepl("Actifs", Libellé) ~ "Active workers, including apprenticeships or paid internships.",
    grepl("Chômeurs", Libellé) ~ "Unemployed",
    grepl("Retraités|prérétaités", Libellé) ~ "Retirees or early retirees",
    grepl("Élèves|étudiants|stagiaires", Libellé) ~ "Students, unpaid trainees aged 14 or older",
    grepl("Moins de 14 ans", Libellé) ~ "Under 14 years old",
    grepl("Femmes|hommes au foyer", Libellé) ~ "Homemakers",
    grepl("Autres inactifs", Libellé) ~ "Other inactive people",
    TRUE ~ Libellé  # Default: keep original if no match
  ))



# Display the comparison of unique French values with their translations to check if there is any mistakes
comparison_table <- learn_merged_uncoded %>%
  select(Libellé, act_translated) %>%
  distinct()

# Suprresion of unuseful data
learn_merged_uncoded <- learn_merged_uncoded %>%
  select(-Libellé)
rm(code_act)

################################ Code Household type ###############################
# Import
code_Household_type <- read_csv("Data - source/project-10-files/code/code_Household_type.csv")

#Merging
learn_merged_uncoded <- merge(learn_merged_uncoded, code_Household_type, by.x = "Household_type", by.y = "Code", all.x = TRUE, all.y = FALSE)
sum(is.na(learn_merged_uncoded$Libellé)) #no missing values

# Translation
learn_merged_uncoded <- learn_merged_uncoded %>%
  mutate(Household_type_translated = case_when(
    grepl("Homme vivant seul", Libellé) ~ "Man living alone",
    grepl("Femme vivant seule", Libellé) ~ "Woman living alone",
    grepl("Plusieurs personnes sans famille", Libellé) ~ "Multiple people without family",
    grepl("Famille principale monoparentale composée d'un homme", Libellé) ~ "Single-parent family led by a man",
    grepl("Famille principale monoparentale composée d'une femme", Libellé) ~ "Single-parent family led by a woman",
    grepl("Famille principale composée d'un couple de deux 'actifs", Libellé) ~ "Main family composed of a couple of two active workers",
    grepl("Famille principale composée d'un couple où seul un homme", Libellé) ~ "Main family composed of a couple where only the man is active",
    grepl("Famille principale composée d'un couple où seule une femme", Libellé) ~ "Main family composed of a couple where only the woman is active",
    grepl("Famille principale composée d'un couple d'aucun 'actif", Libellé) ~ "Main family composed of a couple with no active workers",
    TRUE ~ Libellé  # Default: keep original if no match
  ))

comparison_table <- learn_merged_uncoded %>%
  select(Libellé, Household_type_translated) %>%
  distinct()

# Suprresion of unuseful data
learn_merged_uncoded <- learn_merged_uncoded %>%
  select(-Libellé)
rm(code_Household_type)

################################ Code Highest Degree ###############################
# Import
code_Highest_degree <- read_csv("Data - source/project-10-files/code/code_Highest_degree.csv")

# Merging
learn_merged_uncoded <- merge(learn_merged_uncoded, code_Highest_degree, by.x = "Highest_degree", by.y = "Code", all.x = TRUE, all.y = FALSE)
sum(is.na(learn_merged_uncoded$Libellé)) # Check for missing values

# Translation of "Highest_degree"
learn_merged_uncoded <- learn_merged_uncoded %>%
  mutate(Highest_degree_translated = case_when(
    grepl("Pas de scolarité ou arrêt avant la fin du primaire", Libellé) ~ "No schooling or dropout at the end of primary school",
    grepl("CEP", Libellé) ~ "Primary school certificate",
    grepl("BEPC, brevet élémentaire, brevet des collèges", Libellé) ~ "Middle school diploma or equivalent",
    grepl("CAP, BEP ou diplôme de niveau équivalent", Libellé) ~ "Vocational diploma (CAP/BEP or equivalent)",
    grepl("Baccalauréat général ou technologique", Libellé) ~ "General or technological high school diploma",
    grepl("Baccalauréat professionnel", Libellé) ~ "Professional high school diploma",
    grepl("BTS, DUT, Deug", Libellé) ~ "University technical diploma or associate degree",
    grepl("Licence|licence pro|maîtrise", Libellé) ~ "Bachelor's degree or equivalent",
    grepl("Master|DEA|DESS", Libellé) ~ "Master's degree or equivalent",
    grepl("Doctorat", Libellé) ~ "Doctorate or equivalent",
     grepl("Aucun diplôme et scolarité interrompue à la fin du primaire", Libellé) ~ "No degree, interrupted schooling at the end of primary school or before the end of middle-school",
    grepl("au-delà", Libellé) ~ "No degree, completed schooling up to middle school or beyond",
    TRUE ~ Libellé  # Default: keep the original if no match
  ))


# Display the comparison of unique French values with their translations to check if there are any mistakes
comparison_table <- learn_merged_uncoded %>%
  select(Libellé, Highest_degree_translated) %>%
  distinct()

# Suppression of unuseful data
learn_merged_uncoded <- learn_merged_uncoded %>%
  select(-Libellé)
rm(code_Highest_degree)

################################ Code JOB 42 ###############################
# Import
code_JOB_42 <- read_csv("Data - source/project-10-files/code/code_JOB_42.csv")

# Merging
learn_merged_uncoded <- merge(learn_merged_uncoded, code_JOB_42, by.x = "JOB_42", by.y = "Code", all.x = TRUE, all.y = FALSE)
sum(is.na(learn_merged_uncoded$Libellé)) # Check for missing values

# Translation
learn_merged_uncoded <- learn_merged_uncoded %>%
  mutate(JOB_42_translated = case_when(
    grepl("Agriculteurs sur petite exploitation", Libellé) ~ "Small-scale farmers",
    grepl("Agriculteurs sur moyenne exploitation", Libellé) ~ "Medium-scale farmers",
    grepl("Agriculteurs sur grande exploitation", Libellé) ~ "Large-scale farmers",
    grepl("Artisans", Libellé) ~ "Craftsmen",
    grepl("Commerçants et assimilés", Libellé) ~ "Merchants and related trades",
    grepl("Chefs d'entreprise de 10 salariés ou plus", Libellé) ~ "Business owners with 10 or more employees",
    grepl("Professions libérales", Libellé) ~ "Freelancers or independent professionals",
    grepl("Cadres de la fonction publique", Libellé) ~ "Public sector executives",
    grepl("Professeurs, professions scientifiques", Libellé) ~ "Teachers and scientific professionals",
    grepl("Professions de l'information, des arts et des spectacles", Libellé) ~ "Information, arts, and entertainment professionals",
    grepl("Clergé, religieux", Libellé) ~ "Clergy and religious professionals",
    grepl("Cadres administratifs et commerciaux d'entreprise", Libellé) ~ "Corporate administrative and commercial executives",
    grepl("Ingénieurs et cadres techniques d'entreprise", Libellé) ~ "Engineers and technical managers",
    grepl("Techniciens", Libellé) ~ "Technicians",
    grepl("Contremaîtres, agents de maîtrise", Libellé) ~ "Foremen and supervisors",
    grepl("Employés civils et agents de service de la fonction publique", Libellé) ~ "Public sector employees and service agents",
    grepl("Policiers et militaires", Libellé) ~ "Police and military personnel",
    grepl("Employés administratifs d'entreprise", Libellé) ~ "Corporate administrative employees",
    grepl("Employés de commerce", Libellé) ~ "Retail employees",
    grepl("Personnels des services directs aux particuliers", Libellé) ~ "Personal service workers",
    grepl("Ouvriers qualifiés de type industriel", Libellé) ~ "Skilled industrial workers",
    grepl("Ouvriers qualifiés de type artisanal", Libellé) ~ "Skilled artisanal workers",
    grepl("Ouvriers qualifiés de la manutention, du magasinage et du transport", Libellé) ~ "Skilled manual and transport workers",
    grepl("Ouvriers non qualifiés de type industriel", Libellé) ~ "Unskilled industrial workers",
    grepl("Ouvriers non qualifiés de type artisanal", Libellé) ~ "Unskilled artisanal workers",
    grepl("Ouvriers agricoles", Libellé) ~ "Agricultural workers",
    grepl("Chauffeurs", Libellé) ~ "Drivers",
    grepl("Anciens agriculteurs exploitants", Libellé) ~ "Retired farmers",
    grepl("Anciens artisans, commerçants, chefs d'entreprise", Libellé) ~ "Retired craftsmen, merchants, and business owners",
    grepl("Anciens cadres", Libellé) ~ "Retired executives",
    grepl("Anciens employés", Libellé) ~ "Retired employees",
    grepl("Anciens ouvriers", Libellé) ~ "Retired workers",
    grepl("Chômeurs n'ayant jamais travaillé", Libellé) ~ "Unemployed who have never worked",
    grepl("tudiant", Libellé) ~ "Students",
    grepl("de moins de 60 ans", Libellé) ~ "People without professional activity under 60 (excluded Retired ppl)",
    grepl("Personnes diverses sans activité professionnelle de 60 ans et plus", Libellé) ~ "People without professional activity 60 and older (excluded Retired ppl)",
    grepl("Professeurs des écoles, instituteurs et assimilés", Libellé) ~ "Primary school teachers, instructors, and related professions",
  grepl("Professions intermédiaires de la santé et du travail social", Libellé) ~ "Intermediate health and social work professions",
  grepl("Clergé religieux", Libellé) ~ "Clergy and religious professionals",
  grepl("Professions intermédiaires administratives de la fonction publique", Libellé) ~ "Intermediate administrative professions in public administration",
  grepl("Professions intermédiaires administratives et commerciales des entreprises", Libellé) ~ "Intermediate administrative and commercial professions in companies",
  grepl("Anciennes professions intermédiaires", Libellé) ~ "Former intermediate professions",
  grepl("du travail social", Libellé) ~ "Intermediate health and social work professionals",
    TRUE ~ Libellé  # Default: keep original if no match
  ))



# Display the comparison of unique French values with their translations to check if there are any mistakes
comparison_table <- learn_merged_uncoded %>%
  select(Libellé, JOB_42_translated) %>%
  distinct()

# Suppression of unuseful data
learn_merged_uncoded <- learn_merged_uncoded %>%
  select(-Libellé)
rm(code_JOB_42)

```

```{r Addition_of_the_translation_of_the_code_part_two, results = "hide"}

################################ Code LAST JOB 42 ###############################
# Import
code_JOB_42 <- read_csv("Data - source/project-10-files/code/code_JOB_42.csv")

# Merging
learn_merged_uncoded <- merge(learn_merged_uncoded, code_JOB_42, by.x = "LAST_JOB_42", by.y = "Code", all.x = TRUE, all.y = FALSE)
sum(is.na(learn_merged_uncoded$Libellé)) # Check for missing values

# Translation
learn_merged_uncoded <- learn_merged_uncoded %>%
  mutate(LAST_JOB_42_translated = case_when(
    grepl("Agriculteurs sur petite exploitation", Libellé) ~ "Small-scale farmers",
    grepl("Agriculteurs sur moyenne exploitation", Libellé) ~ "Medium-scale farmers",
    grepl("Agriculteurs sur grande exploitation", Libellé) ~ "Large-scale farmers",
    grepl("Artisans", Libellé) ~ "Craftsmen",
    grepl("Commerçants et assimilés", Libellé) ~ "Merchants and related trades",
    grepl("Chefs d'entreprise de 10 salariés ou plus", Libellé) ~ "Business owners with 10 or more employees",
    grepl("Professions libérales", Libellé) ~ "Freelancers or independent professionals",
    grepl("Cadres de la fonction publique", Libellé) ~ "Public sector executives",
    grepl("Professeurs, professions scientifiques", Libellé) ~ "Teachers and scientific professionals",
    grepl("Professions de l'information, des arts et des spectacles", Libellé) ~ "Information, arts, and entertainment professionals",
    grepl("Clergé, religieux", Libellé) ~ "Clergy and religious professionals",
    grepl("Cadres administratifs et commerciaux d'entreprise", Libellé) ~ "Corporate administrative and commercial executives",
    grepl("Ingénieurs et cadres techniques d'entreprise", Libellé) ~ "Engineers and technical managers",
    grepl("Techniciens", Libellé) ~ "Technicians",
    grepl("Contremaîtres, agents de maîtrise", Libellé) ~ "Foremen and supervisors",
    grepl("Employés civils et agents de service de la fonction publique", Libellé) ~ "Public sector employees and service agents",
    grepl("Policiers et militaires", Libellé) ~ "Police and military personnel",
    grepl("Employés administratifs d'entreprise", Libellé) ~ "Corporate administrative employees",
    grepl("Employés de commerce", Libellé) ~ "Retail employees",
    grepl("Personnels des services directs aux particuliers", Libellé) ~ "Personal service workers",
    grepl("Ouvriers qualifiés de type industriel", Libellé) ~ "Skilled industrial workers",
    grepl("Ouvriers qualifiés de type artisanal", Libellé) ~ "Skilled artisanal workers",
    grepl("Ouvriers qualifiés de la manutention, du magasinage et du transport", Libellé) ~ "Skilled manual and transport workers",
    grepl("Ouvriers non qualifiés de type industriel", Libellé) ~ "Unskilled industrial workers",
    grepl("Ouvriers non qualifiés de type artisanal", Libellé) ~ "Unskilled artisanal workers",
    grepl("Ouvriers agricoles", Libellé) ~ "Agricultural workers",
    grepl("Chauffeurs", Libellé) ~ "Drivers",
    grepl("Anciens agriculteurs exploitants", Libellé) ~ "Retired farmers",
    grepl("Anciens artisans, commerçants, chefs d'entreprise", Libellé) ~ "Retired craftsmen, merchants, and business owners",
    grepl("Anciens cadres", Libellé) ~ "Retired executives",
    grepl("Anciens employés", Libellé) ~ "Retired employees",
    grepl("Anciens ouvriers", Libellé) ~ "Retired workers",
    grepl("Chômeurs n'ayant jamais travaillé", Libellé) ~ "Unemployed who have never worked",
    grepl("tudiant", Libellé) ~ "Students",
    grepl("de moins de 60 ans", Libellé) ~ "People without professional activity under 60 (excluded Retired ppl)",
    grepl("Personnes diverses sans activité professionnelle de 60 ans et plus", Libellé) ~ "People without professional activity 60 and older (excluded Retired ppl)",
    grepl("Professeurs des écoles, instituteurs et assimilés", Libellé) ~ "Primary school teachers, instructors, and related professions",
  grepl("Professions intermédiaires de la santé et du travail social", Libellé) ~ "Intermediate health and social work professions",
  grepl("Clergé religieux", Libellé) ~ "Clergy and religious professionals",
  grepl("Professions intermédiaires administratives de la fonction publique", Libellé) ~ "Intermediate administrative professions in public administration",
  grepl("Professions intermédiaires administratives et commerciales des entreprises", Libellé) ~ "Intermediate administrative and commercial professions in companies",
  grepl("Anciennes professions intermédiaires", Libellé) ~ "Former intermediate professions",
  grepl("du travail social", Libellé) ~ "Intermediate health and social work professionals",
    TRUE ~ Libellé  # Default: keep original if no match
  ))



# Display the comparison of unique French values with their translations to check if there are any mistakes
comparison_table <- learn_merged_uncoded %>%
  select(Libellé, LAST_JOB_42_translated) %>%
  distinct()

# Suppression of unuseful data
learn_merged_uncoded <- learn_merged_uncoded %>%
  select(-Libellé)
rm(code_JOB_42)


################################ Code Emp type ###############################
# Import code
code_emp_type <- read_csv("Data - source/project-10-files/code/code_emp_type.csv")

# Merging
learn_merged_uncoded <- merge(learn_merged_uncoded, code_emp_type, by.x = "emp_type", by.y = "Code", all.x = TRUE, all.y = FALSE)
sum(is.na(learn_merged_uncoded$Libellé))  # Vérification des valeurs manquantes

# Traduction des libellés
learn_merged_uncoded <- learn_merged_uncoded %>%
  mutate(emp_type_translated = case_when(
    grepl("apprentissage", Libellé) ~ "Apprenticeship or professionalization contract",
    grepl("agence d'intérim", Libellé) ~ "Temporary placement through an agency",
    grepl("Emplois aidés", Libellé) ~ "Subsidized jobs (insertion contracts, etc.)",
    grepl("Stagiaires rémunérés", Libellé) ~ "Paid trainees in companies",
    grepl("CDD", Libellé) ~ "Other fixed-term jobs, fixed-term contracts, short-term contracts, seasonal contracts, temporary contracts, etc.",
    grepl("CDI", Libellé) ~ "Permanent contract (CDI)",
    grepl("Non salariés : Indépendants", Libellé, ignore.case = TRUE) ~ "Self-employed: Independents",
    grepl("Non salariés : Employeurs", Libellé, ignore.case = TRUE) ~ "Self-employed: Employers",
    grepl("Non salariés : Aides familiaux", Libellé, ignore.case = TRUE) ~ "Self-employed: Family helpers",
    TRUE ~ Libellé))


# Affichage du tableau comparatif des valeurs uniques pour vérifier les traductions
comparison_table <- learn_merged_uncoded %>%
  select(Libellé, emp_type_translated) %>%
  distinct()

# Suppression des colonnes inutiles
learn_merged_uncoded <- learn_merged_uncoded %>%
  select(-Libellé)

# Optionnel : suppression du dataset si plus nécessaire
rm(code_emp_type)

################################ Code Emp type ###############################
# Import code
code_emp_type <- read_csv("Data - source/project-10-files/code/code_emp_type.csv")

# Merging
learn_merged_uncoded <- merge(learn_merged_uncoded, code_emp_type, by.x = "last_emp_type", by.y = "Code", all.x = TRUE, all.y = FALSE)
sum(is.na(learn_merged_uncoded$Libellé))  # Vérification des valeurs manquantes

# Traduction des libellés
learn_merged_uncoded <- learn_merged_uncoded %>%
  mutate(last_emp_type_translated = case_when(
    grepl("apprentissage", Libellé) ~ "Apprenticeship or professionalization contract",
    grepl("agence d'intérim", Libellé) ~ "Temporary placement through an agency",
    grepl("Emplois aidés", Libellé) ~ "Subsidized jobs (insertion contracts, etc.)",
    grepl("Stagiaires rémunérés", Libellé) ~ "Paid trainees in companies",
    grepl("CDD", Libellé) ~ "Other fixed-term jobs, fixed-term contracts, short-term contracts, seasonal contracts, temporary contracts, etc.",
    grepl("CDI", Libellé) ~ "Permanent contract (CDI)",
    grepl("Non salariés : Indépendants", Libellé, ignore.case = TRUE) ~ "Self-employed: Independents",
    grepl("Non salariés : Employeurs", Libellé, ignore.case = TRUE) ~ "Self-employed: Employers",
    grepl("Non salariés : Aides familiaux", Libellé, ignore.case = TRUE) ~ "Self-employed: Family helpers",
    TRUE ~ Libellé))


# Affichage du tableau comparatif des valeurs uniques pour vérifier les traductions
comparison_table <- learn_merged_uncoded %>%
  select(Libellé, last_emp_type_translated) %>%
  distinct()

# Suppression des colonnes inutiles
learn_merged_uncoded <- learn_merged_uncoded %>%
  select(-Libellé)

# Optionnel : suppression du dataset si plus nécessaire
rm(code_emp_type)

################################ Code Company category ###############################
# Importation
code_company_category <- read_csv("Data - source/project-10-files/code/code_company_category.csv")

# Merging
learn_merged_uncoded <- merge(learn_merged_uncoded, code_company_category, by.x = "company_category", by.y = "Code", all.x = TRUE, all.y = FALSE)
sum(is.na(learn_merged_uncoded$Libellé))  # Vérification des valeurs manquantes

# Translation
learn_merged_uncoded <- learn_merged_uncoded %>%
  mutate(company_category_translated = case_when(
    grepl("Fonction publique d'état", Libellé) ~ "State public service",
    grepl("Fonction publique territoriale", Libellé) ~ "Territorial public service",
    grepl("Fonction publique hospitalière", Libellé) ~ "Public hospital service",
    grepl("Autres organismes publics administratifs", Libellé) ~ "Other public administrative organizations",
    grepl("Personnes morales de droit public", Libellé) ~ "Legal entities under public law subject to commercial law",
    grepl("Entreprises individuelles", Libellé) ~ "Individual enterprises",
    grepl("Données marquées comme issues de pe particuliers employeurs", Libellé) ~ "Data flagged as private individual employers",
    grepl("Organismes privés spécialisés et groupements de droit privé", Libellé) ~ "Private organizations and groups",
    grepl("Autres sociétés privées", Libellé) ~ "Other private companies",
    TRUE ~ Libellé))

# Checking
comparison_table <- learn_merged_uncoded %>%
  select(Libellé, company_category_translated) %>%
  distinct()

# Suppress unused data
learn_merged_uncoded <- learn_merged_uncoded %>%
  select(-Libellé)
rm(code_company_category)

################################ ECO - sect ###############################

# Import du fichier CSV
code_ECO_SECT <- read_csv("Data - source/project-10-files/code/code_ECO_SECT.csv")

learn_merged_uncoded <- learn_merged_uncoded

# Fusion des données
learn_merged_uncoded <- merge(learn_merged_uncoded, code_ECO_SECT, by.x = "ECO_SECT", by.y = "Code", all.x = TRUE, all.y = FALSE)
sum(is.na(learn_merged_uncoded$Libellé))  # Vérification des valeurs manquantes

# Traduction de "ECO_SECT"
learn_merged_uncoded <- learn_merged_uncoded %>%
  mutate(ECO_SECT_translated = case_when(
    grepl("Agriculture, sylviculture et pêche", Libellé) ~ "Agriculture, forestry, and fishing",
    grepl("Industries extractives", Libellé) ~ "Mining and quarrying",
    grepl("Fabrication de denrées alimentaires", Libellé) ~ "Food, beverage, and tobacco manufacturing",
    grepl("Fabrication de textiles", Libellé) ~ "Textile, clothing, leather, and footwear manufacturing",
    grepl("Travail du bois", Libellé) ~ "Woodworking, paper industries, and printing",
    grepl("Cokéfaction et raffinage", Libellé) ~ "Coke and refining",
    grepl("Industrie chimique", Libellé) ~ "Chemical industry",
    grepl("Industrie pharmaceutique", Libellé) ~ "Pharmaceutical industry",
    grepl("Fabrication de produits en caoutchouc", Libellé) ~ "Rubber, plastic, and non-metallic mineral products manufacturing",
    grepl("Métallurgie", Libellé) ~ "Metallurgy and metal products manufacturing (excluding machinery and equipment)",
    grepl("Fabrication de produits informatiques", Libellé) ~ "Manufacture of computer, electronic, and optical products",
    grepl("Fabrication d'équipements électriques", Libellé) ~ "Electrical equipment manufacturing",
    grepl("Fabrication de machines", Libellé) ~ "Manufacture of machinery and equipment",
    grepl("Fabrication de matériels de transport", Libellé) ~ "Manufacture of transport equipment",
    grepl("Autres industries manufacturières", Libellé) ~ "Other manufacturing industries; repair and installation of machinery",
    grepl("Production et distribution d'électricité", Libellé) ~ "Electricity, gas, steam, and air conditioning supply",
    grepl("Production et distribution d'eau", Libellé) ~ "Water supply, sewerage, waste management, and remediation activities",
    grepl("Construction", Libellé) ~ "Construction",
    grepl("Commerce ; réparation d'automobiles", Libellé) ~ "Wholesale, retail trade, and repair of motor vehicles and motorcycles",
    grepl("Transports et entreposage", Libellé) ~ "Transportation and storage",
    grepl("Hébergement et restauration", Libellé) ~ "Accommodation and food service activities",
    grepl("Edition, audiovisuel et diffusion", Libellé) ~ "Publishing, broadcasting, and media",
    grepl("Télécommunications", Libellé) ~ "Telecommunications",
    grepl("Activités informatiques et services d'information", Libellé) ~ "Information technology and information services",
    grepl("Activités financières et d'assurance", Libellé) ~ "Financial and insurance activities",
    grepl("Activités immobilières", Libellé) ~ "Real estate activities",
    grepl("Activités juridiques, comptables", Libellé) ~ "Legal, accounting, management, architecture, engineering, and technical analysis activities",
    grepl("Recherche-développement scientifique", Libellé) ~ "Scientific research and development",
    grepl("Autres activités spécialisées", Libellé) ~ "Other specialized, scientific, and technical activities",
    grepl("Activités de services administratifs", Libellé) ~ "Administrative and support service activities",
    grepl("Administration publique", Libellé) ~ "Public administration",
    grepl("Enseignement", Libellé) ~ "Education",
    grepl("Activités pour la santé humaine", Libellé) ~ "Human health activities",
    grepl("Hébergement médico-social", Libellé) ~ "Residential care and social work activities",
    grepl("Arts, spectacles et activités récréatives", Libellé) ~ "Arts, entertainment, and recreation",
    grepl("Autres activités de services", Libellé) ~ "Other service activities",
    grepl("Activités des ménages en tant qu'employeurs", Libellé) ~ "Household employment activities",
    grepl("Activités extra-territoriales", Libellé) ~ "Extraterrestrial activities",
    TRUE ~ Libellé  # Garder le libellé original si aucune correspondance n'est trouvée
  ))

# Comparaison pour vérifier les traductions
comparison_table <- learn_merged_uncoded %>%
  select(Libellé, ECO_SECT_translated) %>%
  distinct()

# Suppression des colonnes inutiles
learn_merged_uncoded <- learn_merged_uncoded %>%
  select(-Libellé)
rm(code_ECO_SECT)
```

```{r Addition_of_the_translation_of_the_code_part_final, results = "hide"}

################################ Work Condition ###############################
# Translation
learn_merged_uncoded <- learn_merged_uncoded %>%
  mutate(Work_condition_translated = case_when(
    Work_condition == "C" ~ "Full-time",
    Work_condition == "P" ~ "Part-time",
    Work_condition == "N" ~ "Not applicable",
    TRUE ~ Work_condition  # Conserver l'original si aucune correspondance
  ))

# Checking
comparison_table_work_condition <- learn_merged_uncoded %>%
  select(Work_condition, Work_condition_translated) %>%
  distinct()


################################ Job Category ###############################
# Traduction de "job_category"
learn_merged_uncoded <- learn_merged_uncoded %>%
  mutate(job_category_translated = case_when(
    job_category == "O" ~ "Ordinary job",
    job_category == "A" ~ "Apprenticeship",
    job_category == "X" ~ "Other (subsidized job, trainee, unemployment benefit)",
    TRUE ~ job_category  # Conserver l'original si aucune correspondance
  ))

# Comparaison des colonnes originales et traduites pour "job_category"
comparison_table_job_category <- learn_merged_uncoded %>%
  select(job_category, job_category_translated) %>%
  distinct()

print(comparison_table_job_category)

################################ Employee Count ###############################
# Translation and decrypting
learn_merged_uncoded <- learn_merged_uncoded %>%
  mutate(employee_count_translated = case_when(
    employee_count == "tr_0" ~ "0 employee (employees present during the year but not on 31/12)",
    employee_count == "tr_1" ~ "1 to 9 employees",
    employee_count == "tr_2" ~ "10 to 19 employees",
    employee_count == "tr_3" ~ "20 to 49 employees",
    employee_count == "tr_4" ~ "50 to 99 employees",
    employee_count == "tr_5" ~ "100 to 249 employees",
    employee_count == "tr_6" ~ "250 employees and more",
    TRUE ~ employee_count  # Conserver l'original si aucune correspondance
  ))

# Check
comparison_table_employee_count <- learn_merged_uncoded %>%
  select(employee_count, employee_count_translated) %>%
  distinct()

################################ Sup. col. for checking ###############################
rm(comparison_table)
rm(comparison_table_employee_count)
rm(comparison_table_job_category)
rm(comparison_table_work_condition)

################################ Sup. col. original ###############################
columns_to_drop <- c(
  "ECO_SECT", "company_category", "last_emp_type", "emp_type", "LAST_JOB_42", "JOB_42",
  "Highest_degree", "Household_type", "act", "town_type")


learn_merged_uncoded_clean <- learn_merged_uncoded %>%
  select(-all_of(columns_to_drop))


```

```{r results = "hide"}

```

### Understanding the NA

The table below describe the percentage of missing value by variable in the learning set. The value of the main dataset has a 100% completion rate as we saw earmoer/

```{r}
na_percentage_per_column <- learn_merged %>%
  summarise(across(everything(), ~ sum(is.na(.)) / n() * 100)) %>%
  pivot_longer(everything(), names_to = "column_name", values_to = "na_percentage") %>%
  arrange((na_percentage))
na_percentage_per_column
```

#### Missing values regarding employment variables

##### Analysis by activity status

Our first question was to understand whether they are pattern in the messing values. Among several way to deal with missing values Kumar G.R. (2024) quote the use of "Domain-specific knowledge". Similarly, we look at natural relationship between missing values and variable in the main dataset.

The table below count the number of missing values in variables linked to employment by activity status. Several missing cells seem logical corresponding to status where people does not work (housewives, retirees, unemployed and inactive people. "EMP_TYPE" have for example no missing values for active workers but missing values for other active status.

```{r}

na_count_by_act <- learn_merged_uncoded %>%
  group_by(act_translated) %>%
  summarise(
    Remuneration = sum(is.na(remuneration)),
    ECO_SECT = sum(is.na(ECO_SECT)),
    Emp_type = sum(is.na(emp_type)),
    Job_category = sum(is.na(job_category)),
    Job_dep = sum(is.na(Job_dep)),
    Employee_count = sum(is.na(employee_count)),
    Company_category = sum(is.na(company_category)),
    Work_condition = sum(is.na(Work_condition)),
    Working_hours = sum(is.na(Working_hours)),
    TYPE_CONTRACT = sum(is.na(TYPE_CONTRACT))
  ) %>%
  arrange(desc(Remuneration))  

kable(na_count_by_act, caption = "Number of Missing Values by Activity Status")



```

The problem however is that a quarter of missing values in several column correspond to active workers.

```{r}
# All NA per category
total_na_per_column <- learn_merged_uncoded %>%
  summarise(
    Total_Remuneration = sum(is.na(remuneration)),
    Total_ECO_SECT = sum(is.na(ECO_SECT)),
    Total_Emp_type = sum(is.na(emp_type)),
    Total_Job_category = sum(is.na(job_category)),
    Total_Job_dep = sum(is.na(Job_dep)),
    Total_Employee_count = sum(is.na(employee_count)),
    Total_Company_category = sum(is.na(company_category)),
    Total_Work_condition = sum(is.na(Work_condition)),
    Total_Working_hours = sum(is.na(Working_hours)),
    Total_TYPE_CONTRACT = sum(is.na(TYPE_CONTRACT))
  )

# Data in percent
na_percentage_by_act <- learn_merged_uncoded %>%
  group_by(act_translated) %>%
  summarise(
    Remuneration = round(sum(is.na(remuneration)) / total_na_per_column$Total_Remuneration * 100, 0),
    ECO_SECT = round(sum(is.na(ECO_SECT)) / total_na_per_column$Total_ECO_SECT * 100, 0),
    Emp_type = round(sum(is.na(emp_type)) / total_na_per_column$Total_Emp_type * 100, 0),
    Job_category = round(sum(is.na(job_category)) / total_na_per_column$Total_Job_category * 100, 0),
    Job_dep = round(sum(is.na(Job_dep)) / total_na_per_column$Total_Job_dep * 100, 0),
    Employee_count = round(sum(is.na(employee_count)) / total_na_per_column$Total_Employee_count * 100, 0),
    Company_category = round(sum(is.na(company_category)) / total_na_per_column$Total_Company_category * 100, 0),
    Work_condition = round(sum(is.na(Work_condition)) / total_na_per_column$Total_Work_condition * 100, 0),
    Working_hours = round(sum(is.na(Working_hours)) / total_na_per_column$Total_Working_hours * 100, 0),
    TYPE_CONTRACT = round(sum(is.na(TYPE_CONTRACT)) / total_na_per_column$Total_TYPE_CONTRACT * 100, 0)
  ) %>%
  arrange(desc(Remuneration))


kable(na_percentage_by_act, caption = "Percentage of Missing Values by Activity Status (Percentage relatively to the column)")

```

##### Zoom on active workers

To be more precise, as we can see below, in average 20% of the employment data for Active workers are missing in several variables.

```{r}
# Keep only line corresponding to active worker."
active_workers_data <- learn_merged_uncoded %>%
  filter(act == "ACT1.1")

# Calcul du pourcentage de valeurs manquantes et non manquantes pour chaque variable
active_workers_na_percentage <- active_workers_data %>%
  summarise(
    Remuneration_sep_missing = round(sum(is.na(remuneration)) / n() * 100, 0),
    Remuneration_sep_not_missing = round(sum(!is.na(remuneration)) / n() * 100, 0),
    ECO_SECT_sep_missing = round(sum(is.na(ECO_SECT)) / n() * 100, 0),
    ECO_SECT_sep_not_missing = round(sum(!is.na(ECO_SECT)) / n() * 100, 0),
    Emp_type_sep_missing = round(sum(is.na(emp_type)) / n() * 100, 0),
    Emp_type_sep_not_missing = round(sum(!is.na(emp_type)) / n() * 100, 0),
    Job_category_sep_missing = round(sum(is.na(job_category)) / n() * 100, 0),
    Job_category_sep_not_missing = round(sum(!is.na(job_category)) / n() * 100, 0),
    Job_dep_sep_missing = round(sum(is.na(Job_dep)) / n() * 100, 0),
    Job_dep_sep_not_missing = round(sum(!is.na(Job_dep)) / n() * 100, 0),
    Employee_count_sep_missing = round(sum(is.na(employee_count)) / n() * 100, 0),
    Employee_count_sep_not_missing = round(sum(!is.na(employee_count)) / n() * 100, 0),
    Company_category_sep_missing = round(sum(is.na(company_category)) / n() * 100, 0),
    Company_category_sep_not_missing = round(sum(!is.na(company_category)) / n() * 100, 0),
    Work_condition_sep_missing = round(sum(is.na(Work_condition)) / n() * 100, 0),
    Work_condition_sep_not_missing = round(sum(!is.na(Work_condition)) / n() * 100, 0),
    Working_hours_sep_missing = round(sum(is.na(Working_hours)) / n() * 100, 0),
    Working_hours_sep_not_missing = round(sum(!is.na(Working_hours)) / n() * 100, 0),
    TYPE_CONTRACT_sep_missing = round(sum(is.na(TYPE_CONTRACT)) / n() * 100, 0),
    TYPE_CONTRACT_sep_not_missing = round(sum(!is.na(TYPE_CONTRACT)) / n() * 100, 0)
  )

# Transposing
active_workers_na_percentage <- active_workers_na_percentage %>%
  pivot_longer(
    everything(),
    names_to = c("Variable", "Status"),
    names_sep = "_sep_"
  ) %>%
  pivot_wider(
    names_from = "Status",
    values_from = "value"
  )%>%
  rename(
    `Missing values` = missing,
    `Non-missing value` = not_missing
  )


kable(active_workers_na_percentage, caption = "Percentage of missing Values for active workers")


```

###### Data by employment type

```{r}
#Reminder  acvite_worker_data is computed through active_workers_data learn_merged_uncoded %>% filter(act == "ACT1.1")


aw_na_by_emptype_percent <- active_workers_data %>%
  group_by(emp_type_translated) %>%
  summarise(
    Remuneration = round(sum(is.na(remuneration)) / n() * 100, 0),
    ECO_SECT = round(sum(is.na(ECO_SECT)) / n() * 100, 0),
    Job_category = round(sum(is.na(job_category)) / n() * 100, 0),
    Job_dep = round(sum(is.na(Job_dep)) / n() * 100, 0),
    Employee_count = round(sum(is.na(employee_count)) / n() * 100, 0),
    Company_category = round(sum(is.na(company_category)) / n() * 100, 0),
    Work_condition = round(sum(is.na(Work_condition)) / n() * 100, 0),
    Working_hours = round(sum(is.na(Working_hours)) / n() * 100, 0),
    TYPE_CONTRACT = round(sum(is.na(TYPE_CONTRACT)) / n() * 100, 0)
  ) %>% 
  arrange(desc(Remuneration))

kable(aw_na_by_emptype_percent, caption = "Percentage of Missing Values by Employment type")
```

###### Data by Job 42

We try to go further in the analysis by identifying if using the variable "JOB_42" we found some logical pattern. Some categories have a low percentage of missing values.

```{r}
#Reminder  acvite_worker_data is computed through active_workers_data learn_merged_uncoded %>% filter(act == "ACT1.1")


aw_na_by_job_percent <- active_workers_data %>%
  group_by(JOB_42_translated) %>%
  summarise(
    Remuneration = round(sum(is.na(remuneration)) / n() * 100, 0),
    ECO_SECT = round(sum(is.na(ECO_SECT)) / n() * 100, 0),
    Job_category = round(sum(is.na(job_category)) / n() * 100, 0),
    Job_dep = round(sum(is.na(Job_dep)) / n() * 100, 0),
    Employee_count = round(sum(is.na(employee_count)) / n() * 100, 0),
    Company_category = round(sum(is.na(company_category)) / n() * 100, 0),
    Work_condition = round(sum(is.na(Work_condition)) / n() * 100, 0),
    Working_hours = round(sum(is.na(Working_hours)) / n() * 100, 0),
    TYPE_CONTRACT = round(sum(is.na(TYPE_CONTRACT)) / n() * 100, 0)
  ) %>% 
  arrange(desc(Remuneration))

kable(aw_na_by_job_percent, caption = "Percentage of Missing Values by Job 42 Translated for ACT1.1")
```

```{r}
aw_na_by_job_n <- active_workers_data %>%
  group_by(JOB_42_translated) %>%
  summarise(
    Remuneration = round(sum(is.na(remuneration)), 0),
    ECO_SECT = round(sum(is.na(ECO_SECT)), 0),
    Emp_type = round(sum(is.na(emp_type)), 0),
    Job_category = round(sum(is.na(job_category)), 0),
    Job_dep = round(sum(is.na(Job_dep)), 0),
    Employee_count = round(sum(is.na(employee_count)), 0),
    Company_category = round(sum(is.na(company_category)), 0),
    Work_condition = round(sum(is.na(Work_condition)), 0),
    Working_hours = round(sum(is.na(Working_hours)), 0),
    TYPE_CONTRACT = round(sum(is.na(TYPE_CONTRACT)), 0)
  )

kable(aw_na_by_job_n, caption = "Number of Missing Values by Job 42 Translated for ACT1.1")
```

```{r}

```

###### Data by the binary variable "Studying"

No clear pattern where found for studying alone.

```{r}
aw_na_by_job_studying <- active_workers_data %>%
  group_by(Studying) %>%
  summarise(
    Remuneration = round(sum(is.na(remuneration)) / n() * 100, 0),
    ECO_SECT = round(sum(is.na(ECO_SECT)) / n() * 100, 0),
    Job_category = round(sum(is.na(job_category)) / n() * 100, 0),
    Job_dep = round(sum(is.na(Job_dep)) / n() * 100, 0),
    Employee_count = round(sum(is.na(employee_count)) / n() * 100, 0),
    Company_category = round(sum(is.na(company_category)) / n() * 100, 0),
    Work_condition = round(sum(is.na(Work_condition)) / n() * 100, 0),
    Working_hours = round(sum(is.na(Working_hours)) / n() * 100, 0),
    TYPE_CONTRACT = round(sum(is.na(TYPE_CONTRACT)) / n() * 100, 0)
  ) %>% 
  arrange(desc(Remuneration))

kable(aw_na_by_job_studying, caption = "Percentage of Missing Values regarding whether the individual study or not for ACT1.1")
```
